Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-10-24 Thesis/chapter/062-post-emma.tex
post-emma bad first draft

\subsection{Post-EMMA}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{analyse data with other methods post optimization}
Anova shows that the influence of TCal is significant as shown by the F 
\begin{itemize}
    \item ANOVA (influence of TCal) \texttt{Code/Statistics/sub/anova.R}
    \item lin regression (influence of conc) \texttt{Code/Statistics/sub/linreg.py}
    \item grid search 
    \item KRR (???)
    \item SVM (???)
\end{itemize}

\td{plot the predicted data for variables which should be excluded (Tcal, Vcal,Conc, layers)}

>>>>

\subsection{Post-EMMA}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{analyse data with other methods post optimization}
Anova shows that the influence of TCal is significant as shown by the F 
\begin{itemize}
    \item ANOVA (influence of TCal) \texttt{Code/Statistics/sub/anova.R}
    \item lin regression (influence of conc) \texttt{Code/Statistics/sub/linreg.py}
    \item grid search ???
    \item KRR (???)
    \item SVM (???)
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{Linear Regressin}
I thought that the influnce of $conc$ and $\lambda$ are the biggest, but they are just the smalles absolute values. 
Thus, eventhough $T_{cal}$ might have a smaller coefficient for lin reg, the influence on the dependent variable might be larger. 
The biggest influece on $\rho$ is indeed $T_{cal}$, next with about a third of the influence $T_{doc}$. 
Both $T_{cal}$ and $T_{doc}$ have positive coefficients, i.e. a negative influence on the resistance. 
Then both $\lambda$ and $v_{doc}$ both have about a fift ob the largest influence and a negative influence. 
An indication that the data is strongly tainted by error (see also section \ref{sec:res-anova}) is the low $R^2$ score of 0.41, 
which is (sad but true) even unterboten by the $R^2$ of lin fit of $G$, 0.34. 
The coefficients, though share the signs. 
This is only true if the extended data set is used and therefore again rather by chance. 
It is even more \td{erstaunlich} that EMMA managed to decrease the average of $pG$ an $\rho$ with each generation (see figure \ref{fig:emma-gen}. 
Or was is only luck?

$v_{cal}$ and $\lambda$ are well predicted by linear regression as there is a perfect direct proportionality. 
Was zu erwarten war.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{ANOVA}\label{sec:res-anova}
\Gls{anova} doesn't provide a lot of extra information. 
It bestaetigt that TCal has influence on both G and phd. 
It seems that the probability of getting such data per chance that Tcal has no influence 
(null hypothesis is true) is less then 5\% (even less than 1\%). 
wrong the second is not for phd but for extended data set
but for phd even lower than 0.1 \%

\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{Grid Search}
For \gls{krr} and {svm} I had to find out what the ideal hyper parameters were. 
So, I anstellen a grid search with the following hyperparameters: 
%kernel=["poly","rbf"]#,"sigmoid"]
%C= np.array(range(1,20))*0.05
%degree=range(1,6)
%epsilon= np.array(range(1,20))*0.2
%gamma=[0.0,0.1,1.0,10.0]
%#param = {"kernel":kernel, "C":C, "degree":degree, "epsilon":epsilon, "gamma":gamma }
%C=[1,0.1]; degree=[3]; epsilon=[1,2]; gamma=['scale']
Now what are C,epsilon and gamma?

Since the data set was very small, I could be generous with the grid search even on relatively humble hardware (intel i7-8550U).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{KRR}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{SVM}
\td{plot the predicted data for variables which should be excluded (Tcal, Vcal,Conc, layers)}
\fi
